---
title: 'EDA on #TidyTuesday Makeup Shades Data'
author: "Zhaoshan Duan"
date: "2021-03-30"
output:
  blogdown::html_page
header-includes:
  \usepackage{emo}
categories:
  - rstats
  - tidymodels
tags:
  - rstats
  - TidyTuesday
menu:
  sidebar:
    name: EDA on TidyTuesday Makeup Shades Data
    identifier: EDA on TidyTuesday Makeup Shades Data
    weight: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, warning = FALSE, message = FALSE,
                      echo = TRUE, dpi = 300, cache.lazy = FALSE,
                      tidy = "styler", fig.width = 8, fig.height = 5)
```

```{r}
library(tidyverse)
library(tidytuesdayR)
library(emo)
```

Since this is my first technical post, the goal right now is to get comfortable with, essentially including "codes" in my blog posts. I would like to get familiar with exploratory data analysis using this week's [\#TidyTuesday dasta set](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-03-30/readme.md) on Makeup Shades. This data comes from [The Pudding](https://pudding.cool/), with a corresponding [article](https://pudding.cool/2021/03/foundation-names/) as well as a [github repository](https://github.com/the-pudding/data/tree/master/foundation-names).

***Self-reflection:*** I do have to admit that, as a second-semester graduate students in Data Science with some knowledge of data wrangling in R, I am definitely not yet comfortable with exploratory analysis both from high level understanding and low level syntax.

Exploratory data analysis is an iterative cycle with flexible rules. Now I realize that it requires more creative thinking than I thought as I write this post. I lately resumed my daily work and started to listen to the DataFramed Podcast. Interestingly, this realization of EDA resonates with a segment of what a great Data Scientist is in an episode with Hilary Mason:

> "... framing the questions is where the challenge is... (A great Data Scientist) it's not about whose math is the hardest math, it's really about, 'How do I get to a robust problem definition that I can solve, that will actually give someone an insight they didn't otherwise have?' " [Hilary Mason](https://twitter.com/hmason?ref_src=twsrc%5Egoogle%7Ctwcamp%5Eserp%7Ctwgr%5Eauthor) ([DataFramed](https://www.datacamp.com/community/podcast/data-science-past-present-and-future) - Episode 1, 2018)

(Or Does it? I'm not sure. My opinion about this is based on my current level of knowledge and understanding of the Data Science discipline. It would be interesting for future me to read about this opinion again, if we ever made it into the field. `r emo::ji("ask")` )

I found myself exploring the Makeup Shade data set like a headless chicken. An entire afternoon was wasted as I struggled to find out what other questions can be formulated on this data set while being disturbed from reports of increasing anti-Asian sentiment \#[StopAsianHate](https://www.gofundme.com/f/support-aapi-community-fund). The original article does a fantastic job on revealing anti-POC microagressions in the beauty industry. How "consistently numbering the lightest shades first ... when coupled with the numerous microaggressions marginalized groups face ... becomes part of a larger conversation around how deeper shades, and the folks who wear them, are treated by the beauty industry at large." ([The Naked Truth](https://pudding.cool/2021/03/foundation-names/), March 2021)

Therefore, I decided that I will start simple, and deliberately follow suggestions from [R for Data Science](https://r4ds.had.co.nz/exploratory-data-analysis.html) for this post.

# Exploration

First, let's get the data.

```{r}
tuesdata <- tidytuesdayR::tt_load(2021, week = 14)
tuesdata %>% map(glimpse)
```

The `tuesdata` object contains 5 tibbles. Information about these tibbles are available the [Pudding's github page](https://github.com/the-pudding/data/tree/master/foundation-names#allshadescsv--allshadesr).

Let's look at `allShades`, `allNumbers` and `allCategories` for now since these sets were ones that the authors did visualization on.

```{r}
shade <- tuesdata$allShades
number <- tuesdata$allNumbers
category <- tuesdata$allCategories
```

I will start by two questions:

1.  What type of variation occurs within my variables?
2.  What type of variation occurs within my variables ?

However, I am running out of time today and I haven't even touched on my school works. Resume this on Thursday ?

> "There are no routine statistical questions, only questionable statistical routines"
>
> -   Sir David Cox
